Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'

### 2023-03-20 paper/manuscript.Rmd
prepare manuscript revision

keywords          : "social cognition, individual differences, gaze cues, cognitive development"
wordcount         : "8548"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

To assess such external validity for the TANGO task, we handed out a brief demographic questionnaire to families of our kindergarten and online child sample and asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in daycare, and if yes, (5) since when and (6) for how long on an average day. 
`r sum(vali_sample$nTotal[vali_sample$sample == "socenv"])` families filled out the questionnaire and were included in the analysis.
We used parents' responses to construct different scores suggested in the literature [@peterson2000kindred; @cassidy2005theory], capturing aspects of children’s opportunities for social interaction with adults and peers. 
Only the `predictor age of childcare entry` improved the model fit compared to the null model (see Figure Figure \@ref(fig:fig4)A; for model comparisons, see Supplements). Figure \@ref(fig:fig4)B shows that all other predictor scores were positively linked to gaze understanding. Albeit the effects were weak, they are consistent with the literature.

>>>>

keywords          : "social cognition, individual differences, gaze cues, cognitive development"
wordcount         : "8590"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

To assess such external validity for the TANGO task, we handed out a brief demographic questionnaire to families of our kindergarten and online child sample and asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in daycare, and if yes, (5) since when and (6) for how long on an average day. 
`r sum(vali_sample$nTotal[vali_sample$sample == "socenv"])` families filled out the questionnaire and were included in the analysis.
We used parents' responses to construct different scores suggested in the literature [@peterson2000kindred; @cassidy2005theory], capturing aspects of children’s opportunities for social interaction with adults and peers. 
Only the predictor `age of childcare entry` improved the model fit compared to the null model (see Figure Figure \@ref(fig:fig4)A; for model comparisons, see Supplements). Figure \@ref(fig:fig4)B shows that all other predictor scores were positively linked to gaze understanding. Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see Supplements for distribution characteristics of the predictors). Albeit the effects were weak, they are consistent with the literature.

### 2023-03-20 stats/supplements_validity.Rmd
prepare manuscript revision

```{r socenv_prepareData}
mDataSocenv <- testtrials %>% 
  filter(ageInYears < 6) %>% 
  select(datacollection, studyversion, subjID, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW) %>% 
  group_by(subjID) %>% 
  # so that all models run with same nr of subjects
  drop_na() %>%
  ungroup() %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    hhSibs = scale(siblingsNr, center = TRUE, scale = TRUE),
    sibsChildAged = scale(siblingsChildAged, center = TRUE, scale = TRUE),
    ccAge = scale(childcareAge, center = TRUE, scale = TRUE),
    ccHours = scale(childcareHours, center = TRUE, scale = TRUE),
    hhTotal = scale(householdTotal, center = TRUE, scale = TRUE),
    age = scale(ageInMonths, center = TRUE, scale = TRUE), 
    peerExposure = scale(childcareHours, center = TRUE, scale = TRUE) + scale(siblingsNr, center = TRUE, scale = TRUE),
    pe = scale(peerExposure, center = TRUE, scale = TRUE), 
  ) %>% 
  group_by(datacollection, studyversion, subjID, age, ageInMonths, ageInYears, ccAge, ccHours, hhTotal, hhSibs, sibsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, pe) %>% 
  summarise(
    cor_tango = sum(correctBox),
    n_tango = n()
  ) %>% 
  mutate_if(is.character, as.factor)
```

>>>>

```{r socenv_prepareData}
mDataSocenv <- testtrials %>% 
  filter(ageInYears < 6) %>% 
  select(datacollection, studyversion, subjID, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW) %>% 
  group_by(subjID) %>% 
  mutate(siblingsChildAged = replace(siblingsChildAged, siblingsChildAged == -4, 0)) %>% 
  # so that all models run with same nr of subjects
  drop_na() %>%
  ungroup()

socenv_predictordistributions <- mDataSocenv %>% 
  group_by(subjID) %>% 
  slice(1) %>% 
  select(childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW) %>% 
  rename(
    "Age of childcare entry in months" = childcareAge, 
    "# Children in household aged 0-18" = siblingsNr, 
    "Sibling variety score (Peterson, 2000)" = siblingsVarietyScoreP, 
    "# Children in household aged 1-12" = siblingsChildAged,
    "# Household members" = householdTotal,
    "Average hours spent in childcare per day" = childcareHours, 
    "Sibling variety score (Cassidy et al., 2005)" = siblingsVarietyScoreW,
  ) %>% 
  psych::describe() %>% 
  select(-c(vars, median, trimmed, mad, range))

socenv_predictordistributions
saveRDS(socenv_predictordistributions, file = "../saves/socenv_predictordistributions.rds")

mDataSocenv <- mDataSocenv %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    hhSibs = scale(siblingsNr, center = TRUE, scale = TRUE),
    sibsChildAged = scale(siblingsChildAged, center = TRUE, scale = TRUE),
    ccAge = scale(childcareAge, center = TRUE, scale = TRUE),
    ccHours = scale(childcareHours, center = TRUE, scale = TRUE),
    hhTotal = scale(householdTotal, center = TRUE, scale = TRUE),
    age = scale(ageInMonths, center = TRUE, scale = TRUE), 
    peerExposure = scale(childcareHours, center = TRUE, scale = TRUE) + scale(siblingsNr, center = TRUE, scale = TRUE),
    pe = scale(peerExposure, center = TRUE, scale = TRUE), 
  ) %>% 
  group_by(datacollection, studyversion, subjID, age, ageInMonths, ageInYears, ccAge, ccHours, hhTotal, hhSibs, sibsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, pe) %>% 
  summarise(
    cor_tango = sum(correctBox),
    n_tango = n()
  ) %>% 
  mutate_if(is.character, as.factor)
```

### 2023-03-20 supplements/supplements.Rmd
prepare manuscript revision

  - name          : "Manuel Bohn"
    affiliation   : "1"
  - name          : "Steven Kalinke"
    affiliation   : "1"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
floatsintext      : yes
bibliography      : ["../../references.bib"]
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

knitr::kable(webcam_models, format = "latex", booktabs = TRUE) %>% 
  kable_styling(latex_options = "scale_down")
```

@@

knitr::kable(socenv_results, format = "latex", booktabs = TRUE) %>% 
  kable_styling(latex_options = "scale_down")
```

Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights). The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95% CIs included zero. Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding. The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue. The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.

@@

```{r orev_results, results = "asis"}
orev_results <- readRDS("../saves/socenv_results.rds") %>% 
  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
  mutate_if(is.numeric, round, 2)

knitr::kable(orev_results, format = "latex", booktabs = TRUE) %>% 
  kable_styling(latex_options = "scale_down")
```

@@

kable(adult_sample_countryn, "latex", booktabs = TRUE, longtable = TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

>>>>

  - name          : "Manuel Bohn"
    affiliation   : "1"
  - name          : "Steven Kalinke"
    affiliation   : "1"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
floatsintext      : yes
bibliography      : ["../../references.bib"]
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

knitr::kable(webcam_models, format = "latex", booktabs = TRUE) %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
```

@@

knitr::kable(socenv_results, format = "latex", booktabs = TRUE) %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
```

Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights). The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95% CIs included zero. Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding. The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue. The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task. Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see distribution characteristics of predictor variables below).

```{r socenv_predictordistributions, results = "asis"}
socenv_predictordistributions <- readRDS("../saves/socenv_predictordistributions.rds") %>%
  mutate_if(is.numeric, round, 2) %>% 
  ungroup()

socenv_predictordistributions <- socenv_predictordistributions[-1,] # get rid of subjid

knitr::kable(socenv_predictordistributions, format = "latex", booktabs = TRUE) %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
```

@@

```{r orev_results, results = "asis"}
orev_results <- readRDS("../saves/orev_results.rds") %>% 
  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
  mutate_if(is.numeric, round, 2)

knitr::kable(orev_results, format = "latex", booktabs = TRUE) %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
```

@@

kable(adult_sample_countryn, "latex", booktabs = TRUE, longtable = TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
